Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
fix two syntax errors

In order to prove formally that the length of the
kind of hydra battles we consider is not given by a primitive recursive function, we chose to use a formalization of the primitive recursive functions that was originally part of Russell O'Connor's formalization of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

>>>>

In order to prove formally that the length of the
kind of hydra battles we consider is not given by any primitive recursive function, we chose to use a formalization of primitive recursive functions that was originally part of Russell O'Connor's formalization of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.
